---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# GCalcium

Calcium imaging methods produce massive datasets that require immense data manipulation, exploration, and summarizing. GCalcium provides highly-accessible functions to address these issues for both inexperienced and seasoned R users to save researchers time. This package is catered to calcium imaging data, but works with any type of waveform data. A few functions include:

* `format_data` converts a data frame or matrix to a GCalcium-friendly format
* `avg_curve_slope` gets the average slope of curves for a trial
* `between_trial_change` finds the difference in mean activity between trials
* `centered_AUC` finds the area under each curve 
* `moving_window` summarizes data within windows of time

The "Examples" vignette explains all functions in greater detail.

## Installation
```{r, eval = FALSE}
### Install from CRAN repository
install.packages("GCalcium")
```

## Getting started

Since there is currently no ubiquitous way to analyze or format calcium imaging data, most of GCalcium's commands require the data frame to be in "GCalcium format." This is essentially a time series data frame; where the times of recorded signals are in the first row or column, and the observed values of each trial are in the following rows or columns.
```{r, message = FALSE}
### Format data
df.new <- format_data(GCaMP)

### What is the average slope for each curve in trial 1?
cat( avg_curve_slope(Dataframe = df.new, Trial = 1) )

### How does activity of each curve differ from the average in trial 1?
head( centered_AUC(Dataframe = df.new, Trial = 1, FUN = mean) )

### What is the average activity for trial 1 in 0.5 second intervals?
head ( moving_window(Dataframe = df.new, Trial = 1, Window.length = 0.5, FUN = mean) )

### How much does activity differ in the first second of trials 1 & 2, and 3 & 4?
head( between_trial_change(Dataframe = df.new, TrialRange1 = 1:2, TrialRange2 = 3:4, 
                           Time.period = c(0, 1)) )
```
